%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Datadog} % Organization
    {Paris, France} % Location
    {February 2021 - August 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on the backend of the event product.}
        \item {Built high-throughput realtime \textbf{distributed systems} in \textbf{Go (Golang)}, \textbf{Python} and \textbf{Java}, handling more than \textbf{15k events per second}.}
        \item {Integrated open-source monitoring softwares with Datadog's event product.}
        \item {Deployed scalable sevices with \textbf{Kubernetes} and \textbf{Helm}.}
        \item {Developped a distributed rules-based aggregation engine using \textbf{Apache Kafka}.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Backend Engineer Intern} % Job title
    {TicketSwap BV.} % Organization
    {Amsterdam, The Netherlands} % Location
    {July 2019 - November 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed a service architecture for a growth opportunity.}
        \item {Implemented a \textbf{GraphQL API} in Symfony (PHP).}
        \item {Wrote \textbf{automated tests} to maintain a good code quality.}
        \item {Built automated \textbf{CI/CD pipelines} on CircleCI, interacting with \textbf{Docker containers}.}
        \item {Designed a data pipeline for Machine-Learning ticket recognition model using \textbf{Apache Kafka}.}
        \item {Developed a ticket-buying module which interfaces with Dutch and international ticket providers \textbf{third-party APIs}.}
        \item {Imagined and implemented browser notifications for fun and personal knowledge.}
        \item {Sold \textbf{1200 tickets} using the feature during the internship.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
